European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-12 manuscript/manuscript.qmd
future research: 1st

Looking ahead, several promising avenues for future research emerge from our findings. First, examining the mechanisms through which European coordination occurs within the IMF would help illuminate the institutional foundations of the influence we document. Studies of EURIMF and SCIMF activities, European Central Bank participation in IMF decisions, or coordination within G7 and G20 forums could provide valuable insights into the operational aspects of European influence.

>>>>

Looking ahead, several promising avenues for future research emerge from our findings. First, it is worth re-examining the determinants of IMF conditionality by moving beyond simple counts of conditions. In addition to the required fiscal adjustment, future work could measure conditionality across specific domains—such as trade liberalisation, privatisation, or structural reforms—to assess whether transatlantic influence shapes not only the quantity but also the substance of IMF policy requirements.
